---
title: "artyfarty: a quick how-to"
author: "Bart Smeets"
output: 
  md_document:
    fig_height: 4
    fig_width: 6
---

[![Build Status](https://travis-ci.org/Bart6114/artyfarty.svg?branch=master)](https://travis-ci.org/Bart6114/artyfarty)
[![codecov](https://codecov.io/gh/Bart6114/artyfarty/branch/master/graph/badge.svg)](https://codecov.io/gh/Bart6114/artyfarty)


> documentation generated using version `r packageVersion("artyfarty")`

```{r, include=FALSE}
library(artyfarty)
library(ggplot2)
```

`artyfarty` focuses on providing easy access to a few 'nice' ggplot theme, it also includes a number of predefined palettes and watermark convenience functions.

`artyfarty` is a __work in progress__. For now you can install the development version using `devtools`.

```{r, eval=FALSE}
devtools::install_github('bart6114/artyfarty')
```

# Available themes
 
## farty

```{r}

ggplot(diamonds) +
  geom_bar(aes(cut, fill=cut)) +
  theme_farty() +
  ggtitle("Sparkly stones") +
  scale_fill_manual(values = pal("flat"))

ggplot(mtcars) +
  geom_point(aes(x=wt, y=qsec, color=as.factor(cyl))) +
  theme_farty() +
  ggtitle("Vroom") +
  scale_color_manual(values = pal("flat"))


```

## scientific

```{r}

ggplot(diamonds) +
  geom_bar(aes(cut, fill=cut)) +
  theme_scientific() +
  ggtitle("Sparkly stones") +
  scale_fill_manual(values = pal("five38"))

ggplot(mtcars) +
  geom_point(aes(x=wt, y=qsec, color=as.factor(cyl))) +
  theme_scientific() +
  ggtitle("Vroom") +
  scale_color_manual(values = pal("five38"))

```

## monokai

```{r}

ggplot(diamonds) +
  geom_bar(aes(cut, fill=cut)) +
  theme_monokai() +
  ggtitle("Sparkly stones") +
  scale_fill_manual(values = pal("monokai"))


ggplot(mtcars) +
  geom_point(aes(x=wt, y=qsec, color=as.factor(cyl))) +
  theme_monokai() +
  ggtitle("Vroom") +
  scale_color_manual(values = pal("monokai"))

```

## monokai_full

```{r}

ggplot(diamonds) +
  geom_bar(aes(cut, fill=cut)) +
  theme_monokai_full() +
  ggtitle("Sparkly stones") +
  scale_fill_manual(values = pal("monokai"))


ggplot(mtcars) +
  geom_point(aes(x=wt, y=qsec, color=as.factor(cyl))) +
  theme_monokai_full() +
  ggtitle("Vroom") +
  scale_color_manual(values = pal("monokai"))

```


## flat

```{r}

ggplot(diamonds) +
  geom_bar(aes(cut, fill=cut)) +
  theme_flat() +
  ggtitle("Sparkly stones") +
  scale_fill_manual(values = pal("flat"))

ggplot(mtcars) +
  geom_point(aes(x=wt, y=qsec, color=as.factor(cyl))) +
  theme_flat() +
  ggtitle("Vroom") +
  scale_color_manual(values = pal("flat"))

```

## five38

```{r}

ggplot(diamonds) +
  geom_bar(aes(cut, fill=cut)) +
  theme_five38() +
  ggtitle("Sparkly stones") +
  scale_fill_manual(values = pal("five38"))

ggplot(diamonds) +
  geom_bar(aes(cut, fill=cut)) +
  theme_five38(grid_lines = "horizontal") +
  ggtitle("Sparkly stones") +
  scale_fill_manual(values = pal("five38")) +
  coord_flip()

ggplot(mtcars) +
  geom_point(aes(x=wt, y=qsec, color=as.factor(cyl))) +
  theme_five38() +
  ggtitle("Vroom") +
  scale_color_manual(values = pal("five38"))

```

## retro

```{r}

ggplot(diamonds) +
  geom_bar(aes(cut, fill=cut)) +
  theme_retro() +
  ggtitle("Sparkly stones") +
  scale_fill_manual(values = pal("retro"))

ggplot(mtcars) +
  geom_point(aes(x=wt, y=qsec, color=as.factor(cyl))) +
  theme_retro() +
  ggtitle("Vroom") +
  scale_color_manual(values = pal("retro"))

```

## ft

```{r}

ggplot(diamonds) +
  geom_bar(aes(cut, fill=cut)) +
  theme_ft() +
  ggtitle("Sparkly stones") +
  scale_fill_manual(values = pal("ft"))

ggplot(diamonds) +
  geom_bar(aes(cut, fill=cut)) +
  theme_ft(grid_lines = "horizontal") +
  ggtitle("Sparkly stones") +
  scale_fill_manual(values = pal("ft")) +
  coord_flip()

ggplot(mtcars) +
  geom_point(aes(x=wt, y=qsec, color=as.factor(cyl))) +
  theme_ft() +
  ggtitle("Vroom") +
  scale_color_manual(values = pal("ft"))

```

## bain

```{r}

ggplot(diamonds) +
  geom_bar(aes(cut, fill=cut)) +
  theme_bain() +
  ggtitle("Sparkly stones") +
  scale_fill_manual(values = pal("bain"))

ggplot(diamonds) +
  geom_bar(aes(cut, fill=cut)) +
  theme_bain(grid_lines = "horizontal") +
  ggtitle("Sparkly stones") +
  scale_fill_manual(values = pal("bain")) +
  coord_flip()

ggplot(mtcars) +
  geom_point(aes(x=wt, y=qsec, color=as.factor(cyl))) +
  theme_bain() +
  ggtitle("Vroom") +
  scale_color_manual(values = pal("bain"))

```

## economist

```{r}

ggplot(diamonds) +
  geom_bar(aes(cut, fill=cut)) +
  theme_economist() +
  ggtitle("Sparkly stones") +
  scale_fill_manual(values = pal("economist"))

ggplot(diamonds) +
  geom_bar(aes(cut, fill=cut)) +
  theme_economist(grid_lines = "horizontal") +
  ggtitle("Sparkly stones") +
  scale_fill_manual(values = pal("economist")) +
  coord_flip()

ggplot(mtcars) +
  geom_point(aes(x=wt, y=qsec, color=as.factor(cyl))) +
  theme_economist() +
  ggtitle("Vroom") +
  scale_color_manual(values = pal("economist"))

```

## empty

```{r}

ggplot(diamonds) +
  geom_bar(aes(cut, fill=cut)) +
  theme_empty() +
  ggtitle("Sparkly stones") +
  scale_fill_manual(values = pal("flat"))

ggplot(mtcars) +
  geom_point(aes(x=wt, y=qsec, color=as.factor(cyl))) +
  theme_empty() +
  ggtitle("Vroom") +
  scale_color_manual(values = pal("flat"))

```

# Palettes

A number of palettes are available through the `pal()` function. A visual overview can be acquired as follows:

```{r, fig.height=8, fig.width=8}
plot_palettes()
```

Check the `?pal()` documentation for more specifications.

# Watermarks

A watermark might not add much value to a plot, but there are times that you just need to be able to to add a simple watermark.

```{r}
ggplot(diamonds) +
  geom_bar(aes(cut, fill=cut)) +
  theme_retro() +
  ggtitle("Sparkly stones") +
  scale_fill_manual(values = pal("retro")) +
  watermark_img("vignettes/Rlogo.png", location="tl", alpha=.5)
```

```{r}
ggplot(mtcars) +
  geom_point(aes(x=wt, y=qsec, color=as.factor(cyl))) +
  theme_ft() +
  ggtitle("Vroom") +
  scale_color_manual(values = pal("ft")) +
  watermark_txt("watermark", location="br")
```

```{r}
ggplot(mtcars) +
  watermark_txt("watermark", location="center", rot=45, fontsize=36, alpha=.2) +
  geom_point(aes(x=wt, y=qsec, color=as.factor(cyl))) +
  theme_ft() +
  ggtitle("Vroom") +
  scale_color_manual(values = pal("ft"))
```

